### Here you can find a .Rdata file which contains the Dispersal Matrices generated by BioGeoBears for each taxon. However, because the file is to large, you must downloaded in R following the next script.


Download the file 
```{r ,message=FALSE} 
load(url("https://fv2-1.failiem.lv/down.php?i=q7a7a9dh&download_checksum=8d917d213a27b6c128224eecc75d19d73ef3a2cc&download_timestamp=1536126729"))
```


Once the file is downloaded, it appears as a list object called ResultsBioGeoBears

```{r ,message=FALSE}
ResultsBioGeoBears

str(ResultsBioGeoBears)

names(ResultsBioGeoBears)
```
You can explore the results for each taxa, for example, see the M0 results for Cebidae

```{r ,message=FALSE}
ResultsBioGeoBears$Cebidae$M0
```

See the M4 results for Melipona
```{r ,message=FALSE}
ResultsBioGeoBears$Melipona$M4
```


Inside each Matrix (M0, M1, M2, M3 and M4) are a lot of objects, even more lists.You can check what are inside each matrix using this comands.

```{r ,message=FALSE}
str(ResultsBioGeoBears$Cebidae$M2)
summary(ResultsBioGeoBears$Cebidae$M2)
```

Or simply you can check step by step

```{r ,message=FALSE}
names(ResultsBioGeoBears)
names(ResultsBioGeoBears$Stenodermatinae)
names(ResultsBioGeoBears$Stenodermatinae$M3)
```

